An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-04 poly-embed-journal/poly-embed-journal.tex
meeting notes take 2
meeting notes take 3

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\begin{proposition}\label{prop:SL-minimum}
  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.
  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
\end{proposition}
\begin{proof}
	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.

@@

Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
\begin{itemize}
\item Define $u \equiv u'$ if $\Gamma_u = \Gamma_{u'}$
\item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\item $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
\item $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{But well-defined?}
\end{itemize} 
\raf{END NOTES}

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
		\item There is a finite minimum representative set $\U$ for $\Gamma$. \raf{$\trimcover(\Gamma)$ is a finite set (but this is by definition currently)}
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	% \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$, and $\gamma$ is elicitable.\jessiet{At the moment, don't show anything about $\gamma$ elicitable.}\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$? But also, can we pull it out into its own statement? It should follow as a corollary of this and an analogous version of Prop 6.}
\end{restatable}
\begin{proof}
	\jessie{Keep plus example in mind}
	\jessie{Use trim nonredundant and trim covering macros}
	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
	Let $L$ elicit $\Gamma$.

>>>>

% alphabetical order, by convention
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\begin{proposition}\label{prop:SL-minimum}
  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.\raft{Let's change to ``finite representive set''}
  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
\end{proposition}
\begin{proof}
	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.

@@

Let $\L = \{ L:\R\to\reals^\Y_+ \mid L$ has a finite representative set$\}$.

Let $\mathcal{G} =$ set of all properties.
% = \{ \Gamma:\simplex\toto\R \mid \Gamma$ has a finite representative set$\}$.

Defining $\trimnonred(\Gamma)$... say $L$ elicits $\Gamma$
\begin{itemize}
\item Define $u \equiv u'$ if $\Gamma_u = \Gamma_{u'}$
\item $\U_\equiv := \{[u] \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\item $\trimnonred$ for properties: exactly as before: $\trimnonred(\Gamma) = \{\Gamma_u \mid [u] \in \U_\equiv\}$. 
  (old) $:\mathcal{G}\to\mathcal{G}$, $\trimnonred(\Gamma):\simplex \toto \U_\equiv$ where $\trimnonred(\Gamma)_{[u]} := \Gamma_u$, i.e., $\trimnonred(\Gamma)(p) = \{[u] \mid u \in \Gamma(p)\}$. 
\item $\trimnonred:\L \to \L$ given by $\trimnonred(L):\U_\equiv\to\reals^\Y_+$ where $L([u]) = L(u)$.  \raf{Need to prove well-defined (but now it's true)}
\end{itemize} 
\raf{END NOTES}

\begin{restatable}{proposition}{embedtrim}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\Gamma$ embeds a elicitable finite property $\gamma:\simplex \toto \R$.
  \item $\trimnonred(\Gamma)$ is a finite set, and $\cup\,\trimnonred(\Gamma) = \simplex$.
  % \\ $\hat\Gamma := \trimnonred(\Gamma)$ is a finite property, and $\cup\,\hat\Gamma) = \simplex$.
  \item There is a finite minimum representative set $\U$ for $\Gamma$.
  \item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
  \end{enumerate}
  % \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
  Moreover, when any of the above hold, $\trimnonred(\gamma) = \trimnonred(\Gamma) = \{\Gamma_u : u\in\U\} = \Theta$.\jessiet{Also, should this statement be $\trimcover(\gamma) = \trimnonred(\gamma) = \trimcover(\Gamma) = \trimnonred(\Gamma) = \{\Gamma_u \mid u \in \U\} = \Theta$? But also, can we pull it out into its own statement? It should follow as a corollary of this and an analogous version of Prop 6.}
\end{restatable}
\begin{proof}
	\jessie{Keep plus example in mind}
	\jessie{Use trim nonredundant and trim covering macros}
	\jessie{1 -> 2 -> 3 -> 1, 3 <=> 4}
	Let $L$ elicit $\Gamma$.
